---
title: 'Veliki skupovi podataka i etička pitanja'
subtitle: 'Etički kolokvij'
author: 'Denis Vlašiček'
output:
    xaringan::moon_reader:
        nature:
            ratio: '16:9'
            countIncrementalSlides: false
            titleSlideClass: [sectionSlide]
        seal: false
        css: [custom.css, 'animate.css']
---

```{r setup, include=F, echo=F}
library(RefManageR)
library(here)

BibOptions(check.entries = F,
           bib.style = 'authoryear',
           cite.style = 'authoryear',
           style = 'markdown',
           hyperlink = F,
           dashed = F,
           max.names = 1,
           longnamesfirst = F)

bib <- ReadBib(here('prezentacija', 'reference.bib'),
               check = F)
```
class: titleSlide

<script src="https://kit.fontawesome.com/43b8869272.js" crossorigin="anonymous"></script>
 
<div>
    <h1 style="padding-right: 100px; margin-right: 0px; color: var(--background); background: white; padding-top: 50px; padding-bottom: 50px; padding-left: 100px;">
        Istraživačka etika i veliki skupovi podataka
    </h1>
</div>



## Etički kolokvij

### Denis Vlašiček

<span, style='font-family: Comfortaa; font-size: 14pt;'>
    <i class="fab fa-github"></i> vdeni.github.io/eticki-kolokvij
</span>

---

class: sectionSlide, animated, slideInLeft

# Big data

---

class: animated, slideInLeft

## Opis

<hr></hr>

---

class: sectionSlide, animated, slideInLeft

# Prikupljanje

---

class: animated, slideInLeft

## Pristanak

<hr></hr>

---

class: sectionSlide, animated, slideInLeft

# Dijeljenje

---

## Reference

```{r printRefs, results='asis', echo=F}
PrintBibliography(bib)
```
